Heuristics and Really Hard Instances for Subgraph Isomorphism Problems

### 2016-01-26 paper/paper.tex
Little tweaks

\title{Heuristics and Really Hard Instances for Subgraph Isomorphism Problems}
\author{Ciaran McCreesh\thanks{This work was supported by the Engineering and Physical Sciences
    Research Council [grant number EP/K503058/1]} \and Patrick Prosser \and James Trimble \\
University of Glasgow, Glasgow, Scotland \\
c.mccreesh.1@research.gla.ac.uk}

@@

\begin{abstract}
    We show how to generate ``really hard'' random instances for variants of the subgraph
    isomorphism problem. For the non-induced variant, we predict and observe a phase
    transition between satisfiable and unsatisfiable instances, with a corresponding complexity peak
    in three different solvers. For the induced variant, much richer behaviour is observed, and we
    see evidence that constrainedness is a better measure of difficulty than proximity to a phase
    transition. Finally, we show that existing heuristics for the non-induced variant can be
    recovered by determining how to maximise the expected number of solutions, and that this
    technique gives new, better heuristics for the induced variant.
\end{abstract}

@@

Our experiments were performed on systems with Intel Xeon E5-4650 v2 (Q1'14) CPUs and 768GBytes RAM
(although this much RAM was not needed), running Scientific Linux release 6.7.   ?? Software
versions: Clasp 3.1.3, Gurobi 6.0.5, Glasgow, LAD version 2, VFLib. Software was compiled using GCC
4.9.

@@

\section*{Acknowledgements}

?? I suppose Craig could be given an inkling of undeserved gratitude if we have space left.

>>>>

\title{Heuristics and Really Hard Instances for Subgraph Isomorphism Problems}

% \author{Ciaran McCreesh\thanks{This work was supported by the Engineering and Physical Sciences
%     Research Council [grant number EP/K503058/1]} \and Patrick Prosser \and James Trimble \\
% University of Glasgow, Glasgow, Scotland \\
% c.mccreesh.1@research.gla.ac.uk}

\author{First Author \thanks{This work was supported by a small pile of money, but not as much as we
    would have liked.} \and Second Author
    \and Third Author \\
Some Instituion, Somewhere, Some Country \\
anonymous@example.com}

@@

\begin{abstract}
    We show how to generate ``really hard'' random instances for subgraph isomorphism problems. For
    the non-induced variant, we predict and observe a phase transition between satisfiable and
    unsatisfiable instances, with a corresponding complexity peak seen in three different solvers. For
    the induced variant, much richer behaviour is observed, and constrainedness gives
    a better measure of difficulty than proximity to a phase transition. We also discuss variable
    and value ordering heuristics, and their relationship to the expected number of solutions.
\end{abstract}

@@

Our experiments were performed on systems with Intel Xeon E5-4650 v2 CPUs and 768GBytes RAM
(although this much RAM was not needed), running Scientific Linux release 6.7.   ?? Software
versions: Clasp 3.1.3, Gurobi 6.0.5, Glasgow, LAD version 2, VFLib. Software was compiled using GCC
4.9.

@@

% \section*{Acknowledgements}
% 
% Thanks to Kitty Meeks. Also, I suppose Craig could be given an inkling of undeserved gratitude if
% we have space left.
